Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-13 paper.tex

\subsection{Sinkhorn's algorithm}
Iterative Bregman projections onto $\Ccal_1$ and $\Ccal_2$ converge to a point in the intersection $\Ccal_1 \cap \Ccal_2$ \cite{bregman67}. Hence, the so-called Sinkhorn algorithm \cite{sinkhorn64} that realizes alternate Bregman projections, can be considered to compute the regularized  transport matrix:
\begin{align*}
\gamma^0 &= e^{-c/\epsilon} &
\gamma^{l+1} = P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l)),
\end{align*}
and we have 
$\lim_{l\rightarrow +\infty} \gamma^l = P_{\Ccal_1 \cap \Ccal_2}(\gamma^0) = \gamma^*.$

@@

As illustrated in Figure \ref{alternate_projections} (a-b), the Sinkhorn algorithm, that  performs alternate Bregman projections onto the affine sets $\Ccal_1$ and $\Ccal_2$, can be very slow when $\epsilon\to 0$. The idea developped in this paper is to realize over-relaxed projections in order to accelerate the process, as displayed in Figure \ref{alternate_projections} (c)

>>>>

\subsection{Sinkhorn's algorithm}
Iterative Bregman projections onto $\Ccal_1$ and $\Ccal_2$ converge to a point in the intersection $\Ccal_1 \cap \Ccal_2$ \cite{bregman67}. Hence, the so-called Sinkhorn algorithm \cite{sinkhorn64} that performs alternate Bregman projections, can be considered to compute the regularized  transport matrix:
\begin{align*}
\gamma^0 &= e^{-c/\epsilon} &
\gamma^{l+1} = P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l)),
\end{align*}
and we have 
$\lim_{l\rightarrow +\infty} \gamma^l = P_{\Ccal_1 \cap \Ccal_2}(\gamma^0) = \gamma^*.$

@@

As illustrated in Figure \ref{alternate_projections} (a-b), the Sinkhorn algorithm, that  performs alternate Bregman projections onto the affine sets $\Ccal_1$ and $\Ccal_2$, can be very slow when $\epsilon\to 0$. The idea developped in this paper is to perform over-relaxed projections in order to accelerate the process, as displayed in Figure \ref{alternate_projections} (c)
